### 2021-02-13 evaluation.tex
Clean up some todos

The training data consists of examples of the form $(P, \PrecBetter, \PrecWorse)$,
where $P$ is a \gls{cnf} problem and $\PrecBetter, \PrecWorse$ are precedences of symbols of problem $P$
such that out of the two precedences, $\PrecBetter$ yields a proof in fewer iterations of the saturation loop.
\todo{Justify saturation loop iterations as a proxy for success.}
\todo{Reference a detailed explanation of saturation loop iterations.}

@@

The two executions are compared in terms of performance:
predicate precedence $\PrecBetter$ is recognized as better than precedence $\PrecWorse$,
denoted as $\Better{\PrecBetter}{\PrecWorse}$,
if the proof search finishes successfully with $\PrecBetter$ ($\SolverRun{P}{\Prec} = \top$)
and if the number of iterations of the saturation loop with $\PrecBetter$ is smaller than with $\PrecWorse$.
\todo{FB: Use notation for saturation loop iterations if the notation was established earlier.}
If one of the two precedences is recognized as better,
the example $(P, \PrecBetter, \PrecWorse)$ is produced,
where $\PrecBetter$ is the better precedence,
and $\PrecWorse$ is the other precedence.

@@

The problems in $\ProblemsTptp$ are split roughly in half to form the train set and the validation set.
Both training and validation sets are restricted to problems whose graph representation consists of at most \num{100000} nodes
to limit the memory requirements of the training.
The train set is further restricted to problems that correspond to at least one training example.
In total there are \num{7648} problems in the validation set $\ProblemsVal$
and \num{2571} problems in the train set $\ProblemsTrain$.
\todo{FB: Unify the terminology: validation, or train set?}
% /home/filip/projects/vampire-ml/vampire-ml/outputs/2021-02-11/16-27-02/results.csv
% all: 17053
% train: 8527
% val: 8526
% with_questions: 5349
% graphified (not all attempted): 10219
% train&with_questions: 2647
% train&with_questions&graphified: 2571
% val&graphified: 7648
\todo{MS: tady ale lidi bude okamzite zajimat, kolik teda tech problemu na kazde strane zbylo. A jeste by nebylo lepsi vzit nejdriv ty ``male'' problemy a pak teprve pulit.}

@@

\end{tabular}
\end{table*}
\todo{FB: Add links to Neptune runs?}

@@

\todo{Add results for function precedences.}
\todo{Try to evaluate a recommender that uses both predicate and function models.}
\todo{Add discussion.}
\todo{FB: Evaluate on problems larger than 100k nodes.}

>>>>

The training data consists of examples of the form $(P, \PrecBetter, \PrecWorse)$,
where $P$ is a \gls{cnf} problem and $\PrecBetter, \PrecWorse$ are precedences of symbols of problem $P$
such that out of the two precedences, $\PrecBetter$ yields a proof in fewer iterations of the saturation loop.
\todo{FB: Justify saturation loop iterations as a proxy for success.}
\todo{FB: Reference a detailed explanation of saturation loop iterations.}

@@

The two executions are compared in terms of performance:
predicate precedence $\PrecBetter$ is recognized as better than precedence $\PrecWorse$,
denoted as $\Better{\PrecBetter}{\PrecWorse}$,
if the proof search finishes successfully with $\PrecBetter$ ($\SolverRun{P}{\Prec} = \top$)
and if the number of iterations of the saturation loop with $\PrecBetter$ is smaller than with $\PrecWorse$.
\todo{FB: Use notation for saturation loop iterations if the notation was established earlier. If failure is denoted by $\infty$, we can simply use $<$.}
If one of the two precedences is recognized as better,
the example $(P, \PrecBetter, \PrecWorse)$ is produced,
where $\PrecBetter$ is the better precedence,
and $\PrecWorse$ is the other precedence.

@@

The problems in $\ProblemsTptp$ are split roughly in half to form the train set and the validation set.
Both training and validation sets are restricted to problems whose graph representation consists of at most \num{100000} nodes
to limit the memory requirements of the training.
The train set is further restricted to problems that correspond to at least one training example.
In total there are \num{7648} problems in the validation set $\ProblemsVal$
and \num{2571} problems in the train set $\ProblemsTrain$.
\todo{FB: Unify the terminology: validation, or train set?}
% /home/filip/projects/vampire-ml/vampire-ml/outputs/2021-02-11/16-27-02/results.csv
% all: 17053
% train: 8527
% val: 8526
% with_questions: 5349
% graphified (not all attempted): 10219
% train&with_questions: 2647
% train&with_questions&graphified: 2571
% val&graphified: 7648
\todo{MS: jeste by nebylo lepsi vzit nejdriv ty ``male'' problemy a pak teprve pulit.}

@@

\end{tabular}
\end{table*}
\todo{FB: Add links to Neptune runs?}
\todo{FB: Add results for function precedences.}
\todo{FB: Try to evaluate a recommender that uses both predicate and function models.}

@@

\todo{FB: Add discussion.}
\todo{FB: Evaluate on problems larger than 100k nodes.}
